Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

\begin{abstract}
% Problem
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. Several studies show that not all duplication should be refactored. When duplication is refactored, other system attributes may be negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score. Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.

@@

\subsection{Difference from literature clone types}
These proposed definitions slightly differ from type 1, 2 and 3 clones as defined in literature \cite{roy2007survey}. To compare them, we refer to the literature types as T1, T2 and T3 and to our set as T1R (contextually equal clones), T2R (allowing variability) and T3R (gapped clones). Mirroring the literature types, our clone type definitions are subsets of each other:

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:} and will thus require an analysis of the entire system.

>>>>

\begin{abstract}
% Problem
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and it creates implicit dependencies between fragments of code. Several studies show that not all duplication should be refactored. When duplication is refactored, other system attributes may be negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.

% How we fix the problem that we introduced in the first paragraph
We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code. For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) calculated on unit level, which we call the delta maintainability score. Based on this score, we extract common factors between clones and the derived thresholds for them, based on which a developer could filter their clone output.

@@

\subsection{Difference from literature clone types}\label{sec:different-types}
These proposed definitions slightly differ from type 1, 2 and 3 clones as defined in literature \cite{roy2007survey}. To compare them, we refer to the literature types as T1, T2 and T3 and to our set as T1R (contextually equal clones), T2R (allowing variability) and T3R (gapped clones). Mirroring the literature types, our clone type definitions are subsets of each other:

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.
